Self Regulation Ontology Retest Analyses

### 2018-04-27 code/SRO_Retest_Analyses.Rmd
playing around with sem ci s for each subject

```{r}
boot_df
```

>>>>

Step 1: T = Grand mean + ICC * (Subject score - Grand mean)
Step 2: SEP = SD of both measurements * sqrt(1-ICC^2)

```{r}
get_ind_ci = function(dv_var){
  matched = match_t1_t2(dv_var)
  grand_mean = mean(matched$score)
  grand_sd = sd(matched$score)
  dv_icc = get_icc(dv_var)
  sep = grand_sd * sqrt(1-dv_icc^2)
  matched = matched %>% 
    spread(time, score) %>%
    rename("t1"="1", "t2"="2") %>%
    mutate(true_score = grand_mean+dv_icc*(t1-grand_mean),
           ci_up = true_score+sep,
           ci_low = true_score-sep,
           t2_out_ci = ifelse(t2>ci_up|t2<ci_low,1,0),
           prop_dist = abs(t1-t2)/sep,
           large_dist = ifelse(prop_dist>1,1,0))
    return(matched)
}

get_prop_out_ci = function(dv_var){
  get_ind_ci(dv_var) %>%
  summarise(prop_out_ci=sum(t2_out_ci)/n())
}

#Create df of point estimate reliabilities
ind_ci_df <- data.frame(prop_out_ci = rep(NA, length(numeric_cols)))

row.names(ind_ci_df) <- numeric_cols

for(i in 1:length(numeric_cols)){
  ind_ci_df[numeric_cols[i], 'prop_out_ci'] <- get_spearman(numeric_cols[i]) 
}

ind_ci_df$dv = row.names(ind_ci_df)
row.names(ind_ci_df) = seq(1:nrow(ind_ci_df))
ind_ci_df$task = 'task'
ind_ci_df[grep('survey', ind_ci_df$dv), 'task'] = 'survey'
ind_ci_df[grep('holt', ind_ci_df$dv), 'task'] = "task"
ind_ci_df = ind_ci_df %>%
  select(dv, task, prop_out_ci)

ind_ci_df %>%
  filter(prop_out_ci>0.05) %>%
  arrange(-prop_out_ci)

get_ind_ci("five_facet_mindfulness_survey.total")
```
